### 2020-01-24 README.Rmd
- update README urls - fast build for vignette

- See richer examples the package [Tutorial](https://cboettig.github.io/taxadb/articles/intro.html).

- Learn about the underlying data sources and formats in [Data Sources](https://cboettig.github.io/taxadb/articles/articles/data-sources.html)

- Get better performance by selecting an alternative [database backend](https://cboettig.github.io/taxadb/articles/articles/backends.html) engines.

@@

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.

>>>>

- See richer examples the package [Tutorial](https://docs.ropensci.org/taxadb/articles/intro.html).

- Learn about the underlying data sources and formats in [Data Sources](https://docs.ropensci.org/taxadb/articles/articles/data-sources.html)

- Get better performance by selecting an alternative [database backend](https://docs.ropensci.org/taxadb/articles/articles/backends.html) engines.

@@

Please note that this project is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/).
By participating in this project you agree to abide by its terms.
